Pillar 2 - Topic Modeling

### 2019-03-13 Pillar 2 - Topic Modeling.Rmd
perplexity

```
####10-fold Cross-validation
TO BE FINISHED
```{r manual evaluation, cache = TRUE, eval = TRUE}
set.seed(1234)

@@

#NEW
# LDA
```{r LDA fit, cache = TRUE, eval = TRUE}
topic_model <- tibble(

@@

  mutate(
    TM_overview = n_topic %>% map( .f = my_LDA, corpus = d_cast$overview),
    TM_manual   = n_topic %>% map( .f = my_LDA, corpus = d_cast$manuals)
  )
```
##Model Evaluation
Perplexity is a measure of how well a probability model predicts a sample. Thus we need to do cross validation. 
```{r}

#Extracting LDA model n_topics = 2
test1 <- topic_model$TM_overview[1]

#Getting A single LDA Model:
test2 <- test1[[1]]

#getting perplexity
perplexity(test2, d_cast$overview, estimate_theta=FALSE)

Topic <- topics(test2)
Terms <- terms(test2,5)

@@

topics <-  lapply(
  distribution$beta,
  inspect_topics
)
```
##Selectig keywords
```{r key words, eval = TRUE}
get_top_words <- function(d_beta, n = 3){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(n, beta) %>%
    pull(term)%>%
    unique
}

@@

## Visualization
### Functions 
This part is adapted 
```{r LDA prepare, eval = F}
prepare_data_LDA_beta <- function(d_beta){

>>>>

```
####10-fold Cross-validation
NOT NEEDED TO BE FINISHED
```{r manual evaluation, cache = TRUE, eval = TRUE}
set.seed(1234)

@@

```{r LDA fit, cache = TRUE, eval = TRUE}
topic_model <- tibble(

@@

  mutate(
    TM_overview = n_topic %>% map( .f = my_LDA, corpus = d_cast$overview),
    TM_manual   = n_topic %>% map( .f = my_LDA, corpus = d_cast$manuals)
  )
```
##Model Evaluation
###Perplexity
Perplexity is a measure of how well a probability model predicts a sample. Thus we need to do cross validation. 
```{r}

#perplexity Function
my_perplexity <- function(model, d_cast){
  perplexity(model, d_cast, estimate_theta = FALSE)
}

#Get perplexity
topic_test <- topic_model %>%
  mutate(perplex_overview = map(.x = TM_overview, .f = my_perplexity, d_cast$overview),
         perplex_manual   = map(.x = TM_manual,   .f = my_perplexity, d_cast$manual))
```
###log_likelihood
```{r useless stuff}
#Useless stuff:

my_loglike <- function(model){
  return(model@loglikelihood)
}
topic_test %>% mutate(loglike_overview = map(.x = TM_overview, .f = my_loglike)) %>% select(n_topic, loglike_overview)

  for( i in 1:length(topic_model$TM_overview)){
    tmp <- 
  }
}

@@

topics <-  lapply(
  distribution$beta,
  inspect_topics
)
```
#App
##Selectig keywords
```{r key words, eval = TRUE}
get_top_words <- function(d_beta, n = 3){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(n, beta) %>%
    pull(term)%>%
    unique
}

@@

# Visualization
### Functions 
This part is adapted 
```{r LDA prepare, eval = F}
prepare_data_LDA_beta <- function(d_beta){
